### 2019-01-13 writing/thesis/chapters/conclusion.tex
Some more work.
Begin work on introduction/conclusion.

\chapter{Conclusion}
Conclusion here.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../main"
%%% End:

>>>>

\chapter{Conclusion}\label{chap:conclusion}
Conclusion here.

lkjl:
\begin{itemize}
\item We showed in \cref{sec:results-convergence} that our scheme converges for all considered orders for the Navier-Stokes equations.
\item cfd-scenarios competitive results
\item clouds accurate simulated
\item The results of \cref{sec:results-tts-amr} showed, that our \amr{}-criterion is able to save a significant portion of the computational effort compared to a uniformly fine grid.
  It is able to do this without degrading the quality of the solution, even for a scenario that contains small-scale details.
\item Chemical reactions and limiter work for non-stiff detonations.
\end{itemize}

Future work:
\begin{itemize}
\item Improvement of boundary conditions for muscl
\item Due to the \textsc{cfl}-condition,the timestep of our \aderdg{}-scheme scales quadratically with the number of grid cells.
  Even though our \amr{}-criterion is able to reduce the number of needed cells drastically, we could get another large improvement by utilizing local, instead of global timestepping.
\item Our implementation of the \textsc{cj}-detonation wave cannot handle realistic detonations because we do not have an implementation of stiff source terms.
\end{itemize}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../main"
%%% End:

### 2019-01-13 writing/thesis/chapters/introduction.tex
Begin work on introduction/conclusion.

\chapter{Introduction}
We make the following contributions:

\begin{itemize}
\item We implement an \textsc{ader-dg} scheme for the compressible Navier-Stokes equations.
\item We compare different mesh refinement strategies and evaluate their computational efficiency.
\item We investigate the ability of our scheme to simulate classical fluid mechanics test scenarios correctly.
\item We describe the simulation of flows with a background state that is in hydrostatic equilibrium.
  This is useful for problems in atmospheric flow and for problems in meterology.
  Furthermore, we evaluate our discretization for these scenarios.
\end{itemize}

>>>>

\chapter{Introduction}\label{chap:introduction}
We make the following contributions:
\begin{itemize}
\item In \cref{sec:navier-stokes}, we describe a coupling of the compressible Navier-Stokes equations with an advection-diffusion-reaction term for two dimensional problems.
\item We describe an \textsc{ader-dg} (\cref{sec:ader-dg}) and \textsc{muscl}-scheme (\cref{sec:muscl}) for problems with diffusive terms.
  In addition, we describe a combination of both methods in \cref{sec:limiting}, where we use the \textsc{muscl}-scheme in cases where the \textsc{ader-dg}-method is unstable.
\item In \cref{sec:amr}, we introduce a mesh refinement methods that checks, whether the local cell is an outlier.
  As indicator function we use the total variation of the discrete solution and as outlier detection we use the mean and standard variance of this function.
  We evaluate the performance of this method using a time-to-solution test.
\item We investigate the ability of our scheme to simulate classical fluid mechanics test scenarios correctly.
  For this we use a convergence test with a manufactured solution, the Taylor-Green vortex (2d) and the ABC-Flow (3d).
\item We describe the simulation of flows with a background state that is in hydrostatic equilibrium.
  This is useful for problems in atmospheric flow and for problems in meterology.
  Furthermore, we evaluate our discretization for these scenarios using two scenarios that simulate rising bubbles.
\item We show that our method is capable of simulating CJ-detonation waves that are a shock which originates from a chemical reaction.
\end{itemize}
